Data Prep: IUCN and AquaMaps

### 2016-01-15 data_explore/data_prep.Rmd
updated species area table

library(readr)
library(data.table)
library(ggplot2)
library(tidyr)
library(dplyr)
library(stringr)

@@

if(basename(getwd()) != 'data_explore') setwd('data_explore')
source('data_explore_fxns.R')
### When knitting this, it automatically sets WD to be this directory...
### the 'setwd()' is there for running by chunk
```

@@

@@

  create_spp_list(spp_list_base, data_file)
}

@@

>>>>

library(raster)
library(readr)
library(data.table)
library(ggplot2)
library(tidyr)
library(dplyr)
library(stringr)

@@

if(basename(getwd()) != 'data_explore') setwd('~/github/IUCN-AquaMaps/data_explore')
source('data_explore_fxns.R')
### When knitting this, it automatically sets WD to be this directory...
### the 'setwd()' is there for running by chunk
```

@@

loiczid_raster_file  <- file.path(dir_git, 'shiny/data/loiczid_raster.grd')
loiczid_raster       <- raster(loiczid_raster_file)
names(loiczid_raster) <- 'loiczid'

@@

  create_spp_list(spp_list_base, data_file, am_spp_cells, iucn_spp_cells, loiczid_raster)
}

@@

spp_am <- read.csv(file.path(dir_data, 'spp_am.csv'), stringsAsFactors = FALSE)
